---
title: "HW7 Answers"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1

Use squared error loss (a linear model) and the variables waist, age, sex and bmi to predict log(rdi4p + 1). Interpet the coefficients.
```{r multivar}
dat = read.csv("shhs1.txt", header=T, sep="\t")
head(dat)
# using waist, age, sex, bmi to predict log(rdi4p + 1)
y = log(dat$rdi4p + 1)

summary(lm(y ~ waist + age_s1 + gender + bmi_s1, data = dat))
```
Intercept = 
Waist coefficient = 
Age coefficient = 
Gender coefficient = 
BMI coefficient = 


## Question 2

Define sleep disordered breathing as having an rdi4p greater than 15. Use logistic regression to fit a model on having sleep disordered breathing using waist, age, sex and bmi as predictors. Interpret your coefficients.
```{r logit 15}

```


## Question 3

Use a logistic regresion model to predict HTNDerv_S1 using age, sex, bmi and rdi4p. Interpret the rdi4p coefficient.
```{r logit HTNDerv}

```


