---
title: "Airbnb Prices"
output: 
  flexdashboard::flex_dashboard:
    theme: lumen
runtime: shiny

---
<style>                     
.navbar-inverse {
    background-color: white;
    border-color: #FF5A5F;
    color: #FF5A5F;
}

.navbar-inverse .navbar-brand {
    color: #FF5A5F;
}

.navbar-inverse .navbar-nav {
  color: #FF5A5F;
}

</style>  

```{r setup, include=FALSE}
library(flexdashboard); library(tidyverse); library(plotly)
```

Predict
===================================== 

Sidebar {.sidebar}
-------------------------------------

Adjust the sliders below to see what the predicted nightly price of an Airbnb listing with those features would be. This algorithm uses multivariate linear regression and was modelled on a dataset of real Seattle Airbnb listings from 2016. 
```{r inputs}

# Room_type
selectInput("room", "Type of room: ",
            c("Entire home/apt" = "Entire home/apt",
              "Private room" = "Private room",
              "Shared room" = "Shared room"),
            selected = "Entire home/apt")

# Superhost
selectInput("host", "Is the host an Airbnb Superhost? ",
            c("No" = 'f',
              "Yes" = "t"),
            selected = 'f')

# Bedrooms
sliderInput("bedrooms", "Number of bedrooms:",
            min = 0, max = 7, value = 2, step = 1
)
 

# Bathrooms
sliderInput("bathrooms", "Number of bathrooms:",
            min = 0, max = 8, value = 2, step = 0.5
)

# Accommodates
sliderInput("accommodates", "Number of guests it accommodates:",
            min = 1, max = 16, value = 3, step = 1
)

# Reviews
sliderInput("reviews", "Reviews per month:",
            min = 0, max = 13, value = 5, step = 1
)

```

Column {data-width=650}
-------------------------------------

```{r predict}
orig = read.csv("listingsrefined.csv", header=T)

airpre = select(orig, price, room_type, bathrooms, bedrooms, reviews_per_month, accommodates, host_is_superhost)

air = na.omit(airpre)
```

```{r}
# Create Training and Test data -
set.seed(100)  # setting seed to reproduce results of random sampling
trainingRowIndex <- sample(1:nrow(air), 0.8*nrow(air))  # row indices for training data
trainingData <- air[trainingRowIndex, ]  # model training data
testData  <- air[-trainingRowIndex, ]   # test data

lmMod <- glm(price ~ host_is_superhost + room_type + bathrooms + bedrooms + accommodates + reviews_per_month, data=trainingData)  # build the model

pricePred <- predict(lmMod, testData)  # predict price
#summary(lmMod)

actuals_preds <- data.frame(cbind(actuals = testData$price, predicteds = pricePred))  # make actuals_predicteds dataframe.

correlation_accuracy <- cor(actuals_preds)  # 67.6%
min_max_accuracy <- mean(apply(actuals_preds, 1, min) / apply(actuals_preds, 1, max))  
# => 77.6%, min_max accuracy
mape <- mean(abs((actuals_preds$predicteds - actuals_preds$actuals))/actuals_preds$actuals)  
# => 30.9%, mean absolute percentage error
```


```{r plot}

renderPlotly({
  
  # read in user input
  host_is_superhost = input$host
  room_type = input$room
  bathrooms = input$bathrooms
  bedrooms = input$bedrooms
  accommodates = input$accommodates
  reviews_per_month = input$reviews
  
  userInput = data.frame(host_is_superhost, room_type, bathrooms, bedrooms, accommodates, reviews_per_month)
  
  userPred = predict(lmMod, userInput)
  
  # actual vs. predicted y graph
  finalPlot = plot_ly(data = actuals_preds, x = ~actuals, y = ~predicteds) %>% layout(title = "Actual prices vs. algorithm predicted prices of Airbnb listings",
         xaxis = list(title = "Actual listing price ($)"),
         yaxis = list (title = "Algorithm predicted price ($)"))
  
  
  hline <- function(y = 0, color = "#FF5A5F") {
    list(
      type = "line", 
      x0 = 0, 
      x1 = 1, 
      xref = "paper",
      y0 = y, 
      y1 = y, 
      line = list(color = color)
    )
  }
  
  # add prediction from user input
  finalPlot %>% layout(shapes = list(hline(userPred)))
  
})
```

### Predicted Airbnb nightly price, indicated on the graph by the red line {.value-box}
```{r}
renderValueBox({
  host_is_superhost = input$host
  room_type = input$room
  bathrooms = input$bathrooms
  bedrooms = input$bedrooms
  accommodates = input$accommodates
  reviews_per_month = input$reviews
  
  userInput = data.frame(host_is_superhost, room_type, bathrooms, bedrooms, accommodates, reviews_per_month)
  
  userPred = predict(lmMod, userInput)
  prediction = paste('$', ceiling(userPred), " per night")
  
  valueBox(
    value = prediction,
    icon = "fa-money",
    color = "#FF5A5F"
  )
})
```

### Prediction interval: there is a 95% chance that the price of an Airbnb listing with the given features falls in this range {.value-box}
```{r}
renderValueBox({
  host_is_superhost = input$host
  room_type = input$room
  bathrooms = input$bathrooms
  bedrooms = input$bedrooms
  accommodates = input$accommodates
  reviews_per_month = input$reviews
  
  userInput = data.frame(host_is_superhost, room_type, bathrooms, bedrooms, accommodates, reviews_per_month)
  
  userPred = predict(lm(price ~ host_is_superhost + room_type + bathrooms + bedrooms + accommodates + reviews_per_month, data=trainingData), userInput, interval = "predict")
  outcome = data.frame(userPred)
  lwr = paste('$', ceiling(outcome$lwr))
  upr = paste(lwr, ceiling(outcome$upr), sep = '-')
  pi = paste(upr, " per night")
  
  valueBox(
    value = pi,
    icon = "fa-signal",
    color = "primary"
  )
})
```


Visualize
===================================== 
Explore the dataset and relationships of each predictor variable to the outcome variable of price. 

Row {.tabset .tabset-fade}
-------------------------------------
### Number of bedrooms
```{r}
plot_ly(data = air, x = ~bedrooms, y = ~price, color = ~room_type) %>% layout(xaxis = list(title = "Number of bedrooms"),
         yaxis = list (title = "Listing price ($)"))
```

### Number of bathrooms
```{r}
plot_ly(data = air, x = ~bathrooms, y = ~price, color = ~room_type) %>% layout(xaxis = list(title = "Number of bathrooms"),
         yaxis = list (title = "Listing price ($)"))
```

### Number of guests
```{r}
plot_ly(data = air, x = ~accommodates, y = ~price, color = ~room_type) %>% layout(xaxis = list(title = "Number of guests"),
         yaxis = list (title = "Listing price ($)"))
```

### Reviews per month
```{r}

plot_ly(data = air, x = ~reviews_per_month, y = ~price, marker = list(color = "#FF5A5F")) %>% layout(xaxis = list(title = "Reviews per month"),
         yaxis = list (title = "Listing price ($)")) 
```

### Room type
```{r}
avgRoom = air %>%
  group_by(room_type) %>%
  summarise(mean = mean(price), n = n())

plot_ly(data = avgRoom, x = ~room_type, y = ~mean, marker = list(color = "#FF5A5F")) %>% layout(xaxis = list(title = "Listing type"),
         yaxis = list (title = "Average price ($)"))
```


Understand
===================================== 

Column { vertical_layout: scroll}
----------------------------------------------------------
Created by Grace Windheim

- This algorithm uses multivariate linear regression to model the relationship between features of Airbnb listings and their nightly price.
- The data used is from [this dataset](http://insideairbnb.com/get-the-data.html) describing Airbnb listings in Seattle that was sourced from publicly available data on Airbnb's website. This dataset consists of 3815 listings
- Six aspects of Airbnb listings were used as variables to predict the outcome of nightly price:
1. Number of bedrooms
2. Number of bathrooms
3. Number of guests it accommodates
4. Number of reviews the listing receives per month
5. Room type - whether it's an entire house/apt, private room, or shared room
6. Superhost status - whether the host has been designated by Airbnb as a ["Superhost"](https://www.airbnb.com/superhost), someone who is a top-rated and experienced host. 

- The model was built using R's glm function. All coefficients are significant in the model as indicated by the '***' next to each factor:
```{r}
summary(glm(price ~ room_type + bathrooms + bedrooms + accommodates + reviews_per_month + host_is_superhost, data = air))

```

- The model was trained on 80% of the data and tested on the other 20% to yield the predicted prices for each listing. This algorithm had 67.6% accuracy. When plotting the actual prices vs. the algorithm's predicted prices as seen on the 'Predict' tab, we can see that the relationship is fairly linear, but deviates drastically as the listings become more expensive. This could be due to more expensive listings having other features that drive up their value which are not accounted for by the variables in this algorithm, such as location, interior design, or other amenities.

- Below is an example of the actual listing prices vs. the algorithm's predicted prices:
```{r}
head(actuals_preds)
```



